Tropical Andes plant occurrence data GBIF

### 2023-07-18 code/L0/L0_TropicalAndes_plants_GBIF.Rmd
update file path

## Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropAndes_GBIF_plant_occ.csv") 
write.csv(d2, file = TropicalAndes_GBIF_path)
```

>>>>

## Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropicalAndes_GBIF_plant_occ.csv") 
write.csv(d2, file = TropicalAndes_GBIF_path)
```
